Supermartingales and Termination Analysis of Statistical PCF

### 2020-06-12 probabilisticProgrammingMartingales.tex
Summarize the intended results about the alternative semantics.

>>>>

\paragraph{}
The proofs that follow are based on a previous version of $\sim$. I intend to update them after making more progress on the antitone-strict supermartingale completeness result, but for now, here's a summary of the lemmas and theorems I intend to prove about it:
\begin{itemize}
    \item If $M \to N$, the relation $\sim_N^*$ defined on $Rch(N)$ is equal to the restriction of $\sim_M^*$ to $Rch(N)$
    \item Given the definition below of $\Rightarrow$, which is still applicable to this version of $\sim$, and which is the equivalent of $\red$ in this version of the semantics, $\Rightarrow$ is Church-Rosser.
    \item If $M \to N$ at $P$, no position in any term in $Rch(N)$ is related to $(M,P)$ by $\sim_M^*$, and therefore each sample is used at most once in any reduction sequence.
    \item The subprobability distribution of values obtained by reducing a term in the usual call-by-value semantics is equal to that obtained by any reduction strategy on $\Rightarrow$ (i.e.~a sub-relation of $\Rightarrow$ that is a function) (with some allowance made for the fact that some values are not normal forms of $\Rightarrow$, so the reduction strategy might overshoot the value that $\red^\infty$ reaches. I'm not quite sure what form this will take.)
    \item Similarly, the probability of termination is equal in $\red^\infty$ and any reduction strategy on $\Rightarrow$, so almost sure termination can be equivalently defined based on $\Rightarrow$.
    \item For any closed term $N$, if there is any reduction strategy for $N$ and ranking function corresponding to that reduction strategy, $N$ is AST.
    \item Corresponding sparse and antitone-strict ranking function theorems.
\end{itemize}
